---
title: "Wine Master - Data Cleansing"
output: pdf_document
---

```{r}
raw.data <- read.csv("winemag-data-130k-v2.csv")
```

A summary of our data cleansing work:

1. Remove countries with frequency less than 1000
only remain 12 countries in this step.
data dimension from $129971*14$ (because we don't finish the step 4 yet) to $127404*14$$.

2. Extract column year from column title
data dimension from $127404*14$ (because we don't finish the step 4 yet) to $127404*15$.

3. Remove useless columns "Taster Twitter Handle":
data dimension from $127404*15$ to $127404*14$.

4. Remove duplicate rows:
remove rows with the same information on all columns except X.
data dimension from $127404*14$ to $117652*13$.

5. Find out primary keys (used to uniquely match):
assume that ("title"+"variety"+"winery"+"designation") can provide the unique result
unique rows of ("title"+"variety") is the same as unique rows of ("title"+"variety"+"winery"+"designation"), which is 116759, therefore we choose "title" and "variety" as our primary variables.

6. Merge rows group by "Title" and "Variety" (undone)
In this step, we want to compress our data into $116759*14$, which each row of the data frame has unique ("title"+"variety"). 
Specifically, we notice that the unique rows of ("title"+"variety"+ "winery"+ "designation"+ "country"+"province"+"region_1"+ "region_2") = unique rows of ("title"+"variety") = 116759. It implies that we have nothing to do on these 8 varaibles in the step.
In our previous $117652*14$ data, there exists rows with same ("title"+"variety") but different ("points"+"price"+"description"+"taster_name"). In this step, we'll merge the duplicated rows for the same wine by:
i.compute the average of non-NA "points" 
ii.compute the average of non-NA "price" 
iii.concate the text information of "description" 
iv.concate the text information of "taster_name".

Our final data set should be $116759*14$, with "title"+"variety" as primary variables.


#Overview of raw data
```{r message=FALSE, warning=FALSE}
head(raw.data$title)
dim(raw.data)
```


#Remove countries with frequency less than 1000
```{r message=FALSE, warning=FALSE}
data <- raw.data
country.list <- sort(table(data$country), decreasing = TRUE)
country.list <- names(country.list)[country.list > 1000]
data <- data[(data$country %in% country.list),]
dim(data)
```

#Extract column year from column title
```{r message=FALSE, warning=FALSE}
matches <- gregexpr("(1(8|9)[0-9]{2})|(20[0-9]{2})", data$title)
years <- regmatches(data$title, matches)
choose.year <- function(vec) {
  return(max(vec[vec <= 2017]))
}
years.unique <- sapply(years, choose.year)
data$year <- years.unique
table(data$year, exclude = NULL)
```


#Remove the useless column "Taster Twitter Handle"
```{r message=FALSE, warning=FALSE}
data <- subset(data, select = - c(taster_twitter_handle, X))
```

#Remove duplicate rows
```{r message=FALSE, warning=FALSE}
data <- data[!duplicated(data),]
dim(data)
```

#Find out the primary keys (unique name)
```{r message=FALSE, warning=FALSE}
duplicate.title <- names(table(data$title)[table(data$title)>2])
length(duplicate.title) ### the "title" column is not unique
length(unique(data$title))
```

```{r message=FALSE, warning=FALSE}
dim(unique(data[,c("title","variety", "winery", "designation")])) 
### these four variables should give an unique match
dim(unique(data[,c("title","variety")])) 
### we'll use only use "title" and "variety" as our matching standard
```

#Merging rows based on the primary keys ("title" and "variety")
```{r message=FALSE, warning=FALSE}
### We'll merge all rows with the same "title" and "variety"
data$unique_name <- paste(data$title, data$variety)

library(dplyr)
data.recom <- data %>% 
  group_by(unique_name) %>%
  mutate(points = mean(points, na.rm = TRUE), price = mean(price, na.rm = TRUE),
         taster_name = paste(unique(taster_name), collapse = ""),
         description = paste(description, collapse = ""))

data.recom <- data.recom[!duplicated(data.recom),]
data.recom <- as.data.frame(data.recom)
```

```{r message=FALSE, warning=FALSE}
write.csv(data.recom, "wine_data_cleaned.csv")
```



